% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}     

The majority of this thesis was written while travelling across eight countries and three continents. In many ways, this reflects the quantity of experiences I encountered during my doctorate. I feel fortunate enough to not have experienced the stereotypical solitary research life and there are many people I would like to thank for making this work stimulating, challenging and fun.

Firstly, I would like to thank my supervisor, Professor Roberto Cipolla, for his unequivocal guidance and support. He has given my mind substantial room to wander for the last three and a bit years. His enthusiasm for new ideas is relentless, no matter how crazy the idea. Thank you for the wonderful opportunities you have opened for me.

Secondly, I am indebted to the Woolf Fisher Trust for blindly putting faith in my studies and providing the financial support for this research at the University of Cambridge. The community of outstanding New Zealanders they have formed in Cambridge is incredibly inspiring. I hope they continue to support education and push the boundaries of young New Zealanders.

I would like to thank a number of colleagues who I was fortunate to learn from and collaborate with to produce the research in this thesis. In alphabetical order: Abe Bachrach, Vijay Badrinarayanan, Adam Bry, Saumitro Dasgupta, Yarin Gal, Matthew Grimes, Ankur Handa, Peter Henry, Yani Ioannau, Ryan Kennedy, Hayk Martirosyan, Thomas Roddick, Torsten Sattler, Amar Shah and Jamie Shotton.

Thank you to Trinity College, in particular the Trinity College Zoo, for providing a welcoming and supportive community. Most importantly, I would like to thank my family --- Tania, Guy, Fiona and Joce --- and my friends, who kept the conversation scholarly for only what was necessary. In particular, a big thank you to my fianc\'{e}e, Ali Stone, for keeping me alive and motivated throughout this whole adventure.



\end{acknowledgements}
